---
name: Aaron Wenger
date: "`r format(Sys.time(), '%B, %Y')`"
# profilepic: pic.jpg
qualifications: B.S., MA
# position: "Ph.D. Science Education"
address: "Kalamazoo, Michigan"
email: "aaron.wenger@protonmail.com"
#website:
github: ace-wenger
linkedin: aaron-wenger-a6b7b724a
orcid: 000-0002-1972-3001
# aboutme: "I am a post-doctoral fellow with the Science and Mathematics Program Improvement unit with the Mallinson Institute of Science Education at Western Michigan University. I am also a recent graduate of the Mallinson Institute, and I am currently preparing several manuscripts for publication from my dissertation." 
headcolor: e62e00 # for red
docname: CV
output: 
  vitae::awesomecv:
    keep_tex: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Professional Profile
I am a post-doctoral fellow with Science and Mathematics Program Improvement, a unit which is associated with the Mallinson Institute of Science Education at Western Michigan University. 
I am also a recent graduate of the Mallinson Institute.

```{r}
tribble(
  ~ what, ~ dummy, ~ institution, ~ loc, ~ details,
  ## Research Interests
  "Research Interests", "",
  "", "",
  list(
    "1) Role and application of evidence in educational policy and practice",
    "2) Quasi-experimental study designs and their statistical analysis",
    "3) Computational reproducibility and leveraging open source tools/data"
  ),
  ## Teaching and Public Engagement Interests
  "Teaching and Public Engagement Interests", "",
  "", "",
  list(
    "1) Experimental design, causal inference, and the role of evidence in 
    education policy and practice",
    "2) Introductory and advanced biology subjects, particularly microbiology 
    and molecular biology",
    "3) History of educational psychology and science education",
    "4) Statistical and computational research methods using R, esecially 
    computational reproducibility"
  )

) %>% detailed_entries(what, dummy, institution, loc, details)
```

# Education

```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  ## PhD
  "Ph.D. in Science Eduation: Biological Sciences",
  "Western Michigan University",
  "Kalamazoo, Michigan", "2017-2024",
  list(
    "Dissertation: Beyond Average Effects in Education Research: 
    \\textit{Explaining heterogeneity of concept mapping research in science 
    education through meta-regression modeling}. A three-paper dissertation 
    composed of two independent systematic reviews and meta-analyses - third 
    paper is a position paper arguing for the particular uses of meta-analytic 
    methods exemplified by my work",
    "Comittee chaired by Dr. William Cobern, with Dr. Betty Adams and 
    Dr. Ya Zhang"
  ),
  ## Masters
  "M.A. in Biological Sciences",
  "Western Michigan University",
  "Kalamazoo, Michigan", "2017-2021",
  list(
    "Master's Thesis Project: Engineered Flagellin Disulfide Variants in 
    Salmonella typhimurium. Advised by Dr. Brian Tripp",
    "Concurrently enrolled with Ph.D. Science Education program"
  ),
  ## Bachelors
  "B.S. in Biology-Health Sciences - minors in Chemistry, Ancient (History) Studies",
  "Cornerstone University",
  "Grand Rapids, Michigan", "2011-2015",
  list(
    "Senior Thesis Project: a meta-study of the neural crest as a mechanism for vertebrate phenotypic diversity",
    "Internship: Hesse Memorial Archaelogical Laboratory, learned and applied zooarcheological techniques with animal bone remains"
  )
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

\pagebreak

# Research Experience and Certifications

In addition to research experience obtained in the completion of undergraduate, masters, and doctoral degree programs, I have held (or continue to hold) the following notable certifications and research positions.

```{r}
tribble(
  ~ what, ~ when, ~ with, ~ where, ~why,
  ## Graduate Research Assistant in SAMPI
  "Graduate Research Assistant", "2021-2023",
  "Science And Mathematics Program Improvement", "Kalamazoo, Michigan",
  list(
    "Assisted in program evaluation for clients including NSF-funded Professional development for Emerging Education Researchers (PEER) field school,  Kalamazoo Scholars Program, and the Michigan STEM Network (MiSTEM",
    "Created protocols and evaluation tools (e.g., Qualtric surveys and interview questions)",
    "Conducted quantitative and qualitative analysis of numerical, ordinal, and textual data",
    "Wrote internal and external reports summarizing findings"
  ),
  ## Post-doc
  "Post-Doctoral Fellow", "2025-",
  "Science And Mathematics Program Improvement", "Kalamazoo, Michigan",
  list(
    "Conducted evaluation work for the MiSTEM Network, a Michigan Department of Education program for the development of public-private partnerships, teacher prprofessional development, and programs for students to advance STEM education in Michigan", 

    "Created Qualtrics data collection instrument customized with extensive html
    and javascript code",
    "Designed and implemented a relational database to manage many thousands of
    records, and develope data analysis pipelines to derive key program metrics",
    "Collecting and managing various sources of data",
    "Analyzing and making useful visualizations and other resources for data-driven decision-making"
  ),
  ## Certifications
  "Certified Reviewer", "2025",
  "What Works Clearinghouse (WWC)", "",
  "Certified under v5.0 group design standards to conduct reviews of
  experimental and quasi-experimental studies for the WWC",
) %>%
  arrange(desc(when)) %>%
  detailed_entries(what, when, with, where, why)
```

<!-- \pagebreak -->

<!-- # Portfolio and Further Education -->

<!-- ## Software for Statistics and Data Science -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ what, ~ detail, ~ portfolio_link, ~ dummy1, ~ dummy2, -->
<!--   "R", "substantial programming experience with base R, the Rstudio IDE, and common packages such as 'ggplot'", "See \\href{https://github.com/ace-wenger/ConceptMapping_inBioEd}{\\textit{ConceptMapping-inBioEd}}", "", "",  -->
<!--   "Git and GitHub", "substantial experience creating and mangaging projects using Git version control and the GitHub collaboration platform", "See my GitHub account for several public projects", "", "", -->
<!--   "Analysis Pipeline Tools", "substantial experience implementing data analysis pipelines with the `targets` and `renv` R packages", "See \\href{https://github.com/ace-wenger/ConceptMapping_inBioEd}{\\textit{ConceptMapping-inBioEd}}", "", "", -->
<!--   "SPSS and SAS", "minor programming experience with both", "See \\href{https://github.com/ace-wenger/Portfolio/sas}{\\textit{Portfolio/sas}}", "", "",  -->
<!--   "Excel VBA","minor programming experience", "See \\href{https://github.com/ace-wenger/Portfolio/vba}{\\textit{Portfolio/vba}}", "", "" -->
<!-- ) %>%  -->
<!--   brief_entries(glue::glue("\\textbf{<what>}: <detail> (<portfolio_link>)", .open = "<", .close = ">"), .protect = FALSE) -->
<!-- ``` -->

<!-- ## Software for Documentation and Reporting -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ what, ~ detail, ~ portfolio_link, ~ dummy1, ~ dummy2, -->
<!--   "Microsoft Office Suite", "extensive experience with Word, PowerPoint, Excel, Outlook, and Teams", "", "", "", -->
<!--   "Quarto", "substantial experience creating reports and presentations", "", "", "", -->
<!--   "Rmarkdown", "substantial experience creating data analysis notebooks, reports, and other documents such as this CV", "", "", "", -->
<!--   "LaTeX", "minor working experience using the TeXworks IDE such as in this CV", "", "", "", -->
<!-- ) %>%  -->
<!--   brief_entries(glue::glue("\\textbf{<what>}: <detail> (<portfolio_link>)", .open = "<", .close = ">"), .protect = FALSE) -->
<!-- ``` -->

<!-- ## Other Software -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ what, ~ detail, ~ portfolio_link, ~ dummy1, ~ dummy2, -->
<!--   "Qualtrics", "substantial experience in creating survey forms, distributing to program participants, and processing results", "", "", "", -->
<!--   "Google Forms", "substantial experience in creating survey forms and processing results", "", "", "", -->
<!--   "Abstrackr and MetaReviewer", "substantial experience in these platforms for meta-research studies", "", "", "" -->
<!-- ) %>%  -->
<!--   brief_entries(glue::glue("\\textbf{<what>}: <detail> <portfolio_link>", .open = "<", .close = ">"), .protect = FALSE) -->
<!-- ``` -->

<!-- ## Workshops and Online Courses -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ what, ~ detail, ~ semester, ~ dummy1, ~ dummy2, -->
<!--   "Introduction to Systematic Reivew and Meta-Analysis", "a John Hopkins University course hosted by Coursera",  -->
<!--   "2020", "", "", -->

<!--   "AERA-ICPSR PEERS", "attended several in this workshop series including: Modern Meta-analysis, Cutting-edge Quatitative and Computational Methods for STEM Education, and Introduction to qualitative meta-synthesis methods", -->
<!--   "2020-21", "", "", -->

<!--   "Bibliometrics Training Series", "put on by the NIH Library",  -->
<!--   "2021", "", "", -->

<!--   # "Getting Started with SAS Programming", "a SAS course hosted by Coursera", -->
<!--   # "2021", "", "", -->

<!--   "Excel VBA Programming", "video course introducing VBA programming and various applications such as macro implementation, userforms, and webscraping", -->
<!--   "2022", "", "", -->

<!--   # "Hands-on Programming in R", "online book course by Hadley Wickham of Posit", -->
<!--   # "2022", "", "", -->

<!--   # "Happy Git and GitHub for the userR", "online book course introducing basic and more advanced applications of GitHub version control", -->
<!--   # "2022", "", "", -->

<!--   # "Data Science in R", "online book course by Hadley Wickham of Posit", -->
<!--   # "2022", "", "", -->

<!--   "Research Transparency Online Course", "put on by the Berkeley Initiative for Transparency in the Social Sciences (BITSS)", -->
<!--   "2022", "", "", -->

<!--   "Reproducible Research Tutorial Series", "online course by Dr. Schloss of the University of Michigan, supported by NIH", -->
<!--   "2022", "", "", -->

<!--   "Instats: Path analysis with interactions and indirect effects in R", "Taught by Michael Zyphur", -->
<!--   "2022", "", "", -->

<!--   # "The Turing Way", "online community-sourced course supported by the Alan Turing Institute", -->
<!--   # "2023", "", "", -->

<!--   "Instats: Confirmatory factor analysis and structural equation modeling in R", "Taught by Michael Zyphur and with certificate of completion", -->
<!--   "2023", "", "", -->

<!--   "Instats: Meta-analytic structural equation modeling", "Taught by Mike Cheung and with certificate of completion", -->
<!--   "2023", "", "", -->

<!--   "Evidence Synthesis and Meta-Analysis in R (ESMAR) Conference", "several workshops including: Advanced GitHub, Screening studies for eligibility in evidence syntheses", -->
<!--   "2023", "", "" -->
<!-- ) %>%  -->
<!--   arrange(desc(semester)) %>% -->
<!--   brief_entries(glue::glue("\\textbf{<what>}: <detail>", .open = "<", .close = ">"), semester, .protect = FALSE) -->
<!-- ``` -->

# Teaching and Service

```{r}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Graduate Student Panel Reviewer", "2024", "AERA Annual Meeting", "",
  list("Served as graduate student reviewer for Division D (Measurement \\& Research Methodologies) and SIG-SRMA (Systematic Review and Meta-Analysis special interest group)"),
  "Teaching Assistant", "2017-2021", "Western Michigan University", "Kalamazoo, Michigan",
  list(
    "Served as instructor of record, teaching science courses for primary education majors",
    "CHEM 2800 - Physical Science for Elementary Educators: a inquiry-based, activity-centered course covering basic chemical and physical science principles",
    "BIOS 1700 - Life Science for Non-Majors: a laboratory-lecture-based content course covering major topics in the life sciences; taught first as an in-person course then independently adapted to a virtual, partially synchronous implementation for 2020-21 fall/spring semesters",
    "GEOG 1900 - Exploring Earth Science, the Atmosphere: A laboratory-based course covering basic earth science principles with an emphasis on the atmosphere; taught as a virtual, partially synchronous course"
  ),
  "Biology Lecturer for Pre-Med Initiative", "2018", "Western Michigan University", "Kalamazoo, Michigan",
  list("A student-led program for MCAT exam preparation at WMU"),
  "Teacher", "2015-2017", "Friday Addition (FA) and Homeschool Ancillary Program (HsAP)", "Michigan",
  list("Developed and taught 9th grade biology and 7th grade general science classes at FA and HsAP as well as 10th grade chemistry at HsAP"),

  # "College Tutor and Laboratory Assistant", "2012-2015",
  # "Cornerstone University","Grand Rapids, Michigan",
  # list("Tutored college undergraduates for courses in genetics, chemistry, physics, math, and history with 480 hours of experience",
  #      "Assisted in stockroom, ordering materials, organizing activities, and grading laboratory reports"),
) %>%
  arrange(desc(when)) %>%
  detailed_entries(what, when, with, where, why)
```

# Grants and Awards
```{r}
tribble(
  ~what, ~detail, ~when, ~with,
  "Ronald Meyer Academic Scholar",
  "Granted to a student who demonstrates the qualities necessary to become a successful scientist",
  "2014", "Cornerstone University",
  "Graduate Student Research Grant",
  "WMU grant secured for biology master thesis project",
  "2019", "Western Michigan University",
  "Graduate Student Research Grant",
  "WMU grant Secured for science education research project",
  "2021", "Western Michigan University",
  "Department Graduate Research and Creative Scholar",
  "Given in recognition of excellence in research and creative scholarship",
  "2023-2024", "Western Michigan University",
) |>
  arrange(desc(when)) |>
  brief_entries(glue::glue("\\textbf{<what>} \\newline <detail>", .open = "<", .close = ">"), when, with, .protect = FALSE)
```

\pagebreak

# Publications
```{r}
bibliography_entries("Publications.bib")
```

# Presentations
```{r}
bibliography_entries("Presentations.bib")
```

