---
name: Aaron Wenger
date: "`r format(Sys.time(), '%B, %Y')`"
# profilepic: pic.jpg
qualifications: B.S., MA
# position: "Ph.D. Science Education"
address: "Kalamazoo, Michigan"
email: "aaron.wenger@protonmail.com"
www: www.aaroncwenger.com
github: ace-wenger
linkedin: aaron-wenger-a6b7b724a
orcid: 000-0002-1972-3001
# aboutme: "I am a post-doctoral fellow with the Science and Mathematics Program Improvement unit with the Mallinson Institute of Science Education at Western Michigan University. I am also a recent graduate of the Mallinson Institute, and I am currently preparing several manuscripts for publication from my dissertation." 
headcolor: e62e00 # for red
docname: CV
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
# encountered processing/compatibility issue with bibliography_entries()
# renv::install("mitchelloharawild/vitae@6a70d7e")
```

# Professional Profile
I am a post-doctoral fellow with Science and Mathematics Program Improvement (SAMPI), unit which is associated with the Mallinson Institute of Science Education at Western Michigan University (WMU). 
We conduct evaluation work for WMU and for many external partners including NSF grantees and the Michigan Department of Education.
I am also a recent graduate of the Mallinson Institute.

```{r}
tribble(
  ~what, ~dummy, ~institution, ~loc, ~details,
  ## Research Interests
  "Research and Evaluation Interests", "",
  "", "",
  list(
    "1) Role and application of evidence in educational policy and practice",
    "2) Quasi-experimental study designs and their statistical analysis",
    "3) Computational reproducibility and leveraging open source tools/data"
  ),
  # Teaching and Public Engagement Interests
  "Teaching and Public Engagement Interests", "",
  "", "",
  list(
    "1) Education research and the role of evidence in education policy/practice",
    "2) History of educational psychology and implications for teaching practices",
    "3) Introductory and advanced biology subjects",
    "4) Statistical and computational research methods using R"
  )
) |> detailed_entries(what, dummy, institution, loc, details)
```

# Education

```{r}
tribble(
  ~degree, ~uni, ~loc, ~dates, ~details,
  ## PhD
  "Ph.D. in Science Eduation: Biological Sciences",
  "Western Michigan University",
  "Kalamazoo, Michigan", "2017-2024",
  list(
    "Dissertation -- Beyond Average Effects in Education Research: \\textit{Explaining heterogeneity of concept mapping research in science education through meta-regression modeling}",
    "Committee chaired by Dr. William Cobern, with Dr. Betty Adams and Dr. Ya Zhang"
  ),
  ## Masters
  "M.A. in Biological Sciences",
  "Western Michigan University",
  "Kalamazoo, Michigan", "2017-2021",
  list(
    "Master's Thesis Project -- Engineered Flagellin Disulfide Variants in Salmonella typhimurium. Advised by Dr. Brian Tripp",
    "Concurrently enrolled with Ph.D. Science Education program"
  ),
  ## Bachelors
  "B.S. in Biology-Health Sciences - minors in Chemistry, Ancient (History) Studies",
  "Cornerstone University",
  "Grand Rapids, Michigan", "2011-2015",
  list(
    "Senior Thesis Project: Meta-study of the neural crest as a mechanism for vertebrate phenotypic diversity",
    "Internship: Hesse Memorial Archaelogical Laboratory, learned and applied zooarcheological techniques with ancient animal bone remains"
  )
) |> detailed_entries(degree, dates, uni, loc, details)
```

# Academic Appointments

```{r}
tribble(
  ~position, ~when, ~with, ~where, ~details,
  "Post-Doctoral Fellow", "2025-present",
  "Science And Mathematics Program Improvement (SAMPI)", "Kalamazoo, Michigan",
  "\\begin{cvitems}
     \\item Contributed to the evaluation of several education programs both in K-12 and post-secondary education, principally:
     \\item The MiSTEM Network, a Michigan Department of Education program for the development of public-private partnerships, teacher professional development, and programs for students to advance STEM education in Michigan
     \\item MiLEAP Grant, a Michigan Department of Education grant awarded to WMU for the improvement of systems for early detection and academic interventions for at-risk students -- included a retrospective evaluation of The Gardner Institute's \\textit{Gateways to Completion} program at WMU
     \\item See additional description of these projects under \\textsc{Research Experience}
   \\end{cvitems}"
) |> detailed_entries(position, when, with, where, details)
# tribble(
#  ~position, ~when, ~with, ~where, ~what,
#  ## Post-doc
#  "Post-Doctoral Fellow", "2025-present",
#  "Science And Mathematics Program Improvement (SAMPI)", "Kalamazoo, Michigan",
#  list(
#    "statement 1",
#    "statement 2"
#    # "Contributed to the evaluation of several education programs both in K-12 and post-secondary education, principally:",
#    # "The MiSTEM Network, a Michigan Department of Education program for the development of public-private partnerships, teacher professional development, and programs for students to advance STEM education in Michigan",
#    # "MiLEAP Grant, a Michigan Department of Education grant awarded to WMU for the improvement of systems for early detection and academic interventions for at-risk students -- included a retrospective evaluation of The Gardner Institute's \\textit{Gateways to Completion} program at WMU",
#    # "See additional description of these projects under \\textsc{Research Experience}"
#  )
# ) |> detailed_entries(position, when, with, where, what)
# "Created Qualtrics data collection instrument customized with extensive html
# and javascript code",
# "Designed and implemented a relational database to manage many thousands of
# records, and develope data analysis pipelines to derive key program metrics",
# "Collecting and managing various sources of data",
# "Analyzing and making useful visualizations and other resources for data-driven decision-making"
```

# Publications
```{r}
bibliography_entries("articles.bib")
```

## Manuscripts in Preparation
```{r}
bibliography_entries("manuscripts.bib")
```

<!-- ## Other Scholarly Writing
<!-- 
<!-- ### Software
<!-- ### Data
<!-- ### Registered Reports and Protocols
<!-- ### Notable Blog Posts -->

# Presentations
```{r}
bibliography_entries("presentations.bib")
```

# Grants and Awards
```{r}
tribble(
  ~what, ~detail, ~when, ~with,
  # "Ronald Meyer Academic Scholar",
  # "Granted to a student who demonstrates the qualities necessary to become a
  # successful scientist",
  # "2014", "Cornerstone University",
  "Graduate Student Research Grant",
  "WMU grant secured for biology master thesis project",
  "2019", "Western Michigan University",
  "Graduate Student Research Grant",
  "WMU grant Secured for science education research project",
  "2021", "Western Michigan University",
  "Department Graduate Research and Creative Scholar",
  "Given in recognition of excellence in research and creative scholarship",
  "2023-2024", "Western Michigan University",
) |>
  arrange(desc(when)) |>
  brief_entries(
    glue::glue(
      "\\textbf{<what>} \\newline <detail>",
      .open = "<", .close = ">"
    ),
    when, with,
    .protect = FALSE
  )
```

# Teaching and Service
```{r}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Graduate Student Panel Reviewer", "2024", "AERA Annual Meeting", "",
  list("Served as graduate student reviewer for Division D (Measurement \\& Research Methodologies) and SIG-SRMA (Systematic Review and Meta-Analysis special interest group)"),
  "Teaching Assistant", "2017-2021", "Western Michigan University", "Kalamazoo, Michigan",
  list(
    "Served as instructor of record, teaching science courses for primary education majors",
    "CHEM 2800 - Physical Science for Elementary Educators: a inquiry-based, activity-centered course covering basic chemical and physical science principles",
    "BIOS 1700 - Life Science for Non-Majors: a laboratory-lecture-based content course covering major topics in the life sciences; taught first as an in-person course then independently adapted to a virtual, partially synchronous implementation for 2020-21 fall/spring semesters",
    "GEOG 1900 - Exploring Earth Science, the Atmosphere: A laboratory-based course covering basic earth science principles with an emphasis on the atmosphere; taught as a virtual, partially synchronous course"
  ),
  "Biology Lecturer for Pre-Med Initiative", "2018", "Western Michigan University", "Kalamazoo, Michigan",
  list("A student-led program for MCAT exam preparation at WMU"),
  "Teacher", "2015-2017", "Friday Addition (FA) and Homeschool Ancillary Program (HsAP)", "Michigan",
  list("Developed and taught 9th grade biology and 7th grade general science classes at FA and HsAP as well as 10th grade chemistry at HsAP"),

  # "College Tutor and Laboratory Assistant", "2012-2015",
  # "Cornerstone University","Grand Rapids, Michigan",
  # list("Tutored college undergraduates for courses in genetics, chemistry, physics, math, and history with 480 hours of experience",
  #      "Assisted in stockroom, ordering materials, organizing activities, and grading laboratory reports"),
) |>
  arrange(desc(when)) |>
  detailed_entries(what, when, with, where, why)
```

<!-- mentoring -->

# Research Experience and Certifications

In addition to research experience obtained in the completion of degree programs and in academic positions, I have held (or continue to hold) the following notable certifications and research positions.

```{r}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  ## Graduate Research Assistant in SAMPI
  "Graduate Research Assistant", "2021-2023",
  "Science And Mathematics Program Improvement", "Kalamazoo, Michigan",
  list(
    "Assisted in program evaluation for clients including: NSF-funded Professional development for Emerging Education Researchers (PEER) field school; Kalamazoo Scholars Program; and The MiSTEM Network",
    "Created protocols and evaluation tools (e.g., Qualtric surveys and interview questions)",
    "Conducted quantitative and qualitative analysis of numerical, ordinal, and textual data",
    "Wrote internal and external reports summarizing findings"
  ),
  ## Certifications
  "Certified Reviewer", "2025",
  "What Works Clearinghouse (WWC)", "",
  "Certified under v5.0 group design standards to conduct reviews of
  experimental and quasi-experimental studies for the WWC",
) |>
  arrange(desc(when)) |>
  detailed_entries(what, when, with, where, why)
```

# Professional Development and Skills

I value the continous development of my skills and areas of expertise.
The following describes these skills especially with regards to my proficiency with programming languagues, software for statistical analysis, and tools for open and accessible scientific reports.

## Software for Statistics and Data Science

```{r}
tribble(
  ~what, ~detail, ~portfolio_link, ~dummy1, ~dummy2,
  "R",
  "extensive programming experience with base R and many packages",
  "See \\href{https://github.com/ace-wenger/ConceptMapping_inBioEd}{\\textit{ConceptMapping-inBioEd}}",
  "", "",
  "Git and GitHub",
  "substantial experience creating and mangaging projects using Git version control and the GitHub collaboration platform",
  "See my GitHub account for several public projects",
  "", "",
  "Analysis Pipeline Tools", "substantial experience implementing data analysis pipelines with the `targets` and `renv` R packages", "See \\href{https://github.com/ace-wenger/ConceptMapping_inBioEd}{\\textit{ConceptMapping-inBioEd}}", "", "",
  "SPSS and SAS", "minor programming experience with both", "See \\href{https://github.com/ace-wenger/Portfolio/sas}{\\textit{Portfolio/sas}}", "", "",
  "Excel VBA", "minor programming experience", "See \\href{https://github.com/ace-wenger/Portfolio/vba}{\\textit{Portfolio/vba}}", "", ""
) |>
  brief_entries(
    glue::glue(
      "\\textbf{<what>}: <detail> (<portfolio_link>)",
      .open = "<", .close = ">"
    ),
    .protect = FALSE
  )
```

## Software for Documentation and Reporting

```{r}
tribble(
  ~what, ~detail, ~portfolio_link, ~dummy1, ~dummy2,
  "Microsoft Office Suite",
  "extensive collaborative experience, including use of advanced Word features, formulas and VBA macro programs in Excel",
  "", "", "",
  "Google Workspaces",
  "extensive collaborative experience, including use of the API in Drive, Docs, and sheets to integrate R scripts",
  "", "", "",
  "Quarto and Rmarkdown",
  "substantial experience creating reports and presentations that integrate R scripts and render to MS Word, PDF, HTML webpages and dashboards, entire websites, and Google Docs",
  "", "", "",
  "LaTeX",
  "minor experience working with Tex files such as in editing this CV",
  "", "", "",
) %>%
  brief_entries(glue::glue("\\textbf{<what>}: <detail> (<portfolio_link>)", .open = "<", .close = ">"), .protect = FALSE)
```

## Other Software

```{r}
tribble(
  ~what, ~detail, ~portfolio_link, ~dummy1, ~dummy2,
  "Qualtrics", "substantial experience in creating survey forms, customizing those forms with javascript and html, distributing to program participants, and processing results", "", "", "",
  "Google Forms", "substantial experience in creating survey forms and processing results", "", "", "",
  "Abstrackr and MetaReviewer", "substantial experience in these platforms for meta-research studies", "", "", ""
) %>%
  brief_entries(glue::glue("\\textbf{<what>}: <detail> <portfolio_link>", .open = "<", .close = ">"), .protect = FALSE)
```

## Workshops and Online Courses

```{r}
tribble(
  ~what, ~detail, ~semester, ~dummy1, ~dummy2,
  "Introduction to Systematic Reivew and Meta-Analysis",
  "a John Hopkins University course hosted by Coursera",
  "2020", "", "",
  "AERA-ICPSR PEERS",
  "several in this workshop series including: Modern Meta-analysis, Cutting-edge Quatitative and Computational Methods for STEM Education, and Introduction to qualitative meta-synthesis methods",
  "2020-21", "", "",
  "Bibliometrics Training Series",
  "put on by the NIH Library",
  "2021", "", "",
  "Research Transparency Online Course",
  "put on by the Berkeley Initiative for Transparency in the Social Sciences (BITSS)",
  "2022", "", "",
  "Reproducible Research Tutorial Series",
  "online course by Dr. Schloss of the University of Michigan, supported by NIH",
  "2022", "", "",
  "Instats - Path analysis with interactions and indirect effects in R",
  "Taught by Michael Zyphur",
  "2022", "", "",
  "Instats - Confirmatory Factor Analysis and Structural Equation Modeling in R",
  "Taught by Michael Zyphur and with certificate of completion",
  "2023", "", "",
  "Instats - Meta-analytic Structural Equation Modeling in R",
  "Taught by Mike Cheung and with certificate of completion",
  "2023", "", "",

  # "Evidence Synthesis and Meta-Analysis in R (ESMAR) Conference",
  # "several workshops including: Advanced GitHub, Screening studies for eligibility in evidence syntheses",
  # "2023", "", "",

  "Boot.dev - Learn to Code in Python",
  "basic principles of coding in python3",
  "2025", "", "",
  "Boot.dev - Learn Git",
  "version control fundamentals, repository management, git internals, branching, merging, rebasing, remote repositories, and remote collaboration",
  "2025", "", "",
  "Boot.dev - Learn Linux",
  "Linux command line, shell scripting basics, file system management, user permissions and security, I/O redirection and piping, process management, package management, and terminal environments",
  "2025", "", "",
  "Boot.dev - Learn Object-oriented Programming",
  "clean code principles, classes, encapsulation, abstraction, inheritance, and polymorphism",
  "2025", "", "",
  "Boot.dev - Learn Functional Programming",
  "",
  "2026", "", "",
  "Boot.dev - Learn SQL",
  "relational database design, crud operations, SQL queries, joins, subqueries, aggregations, data normalization, and performance and indexing",
  "2025", "", "",
) |>
  arrange(desc(semester), what) %>%
  brief_entries(glue::glue("\\textbf{<what>}: <detail>", .open = "<", .close = ">"), semester, .protect = FALSE)
```




