%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{books}
\name{Aaron C.}{Wenger}
\position{Ph.D. Candidate{\enskip\cdotp\enskip}Mallinson Institute for Science Education} % `xx`was `software architect`
\address{2226 Frederick Ave., Kalamazoo, Michigan 49008}

\mobile{(616) 799-4352}
\email{aaron.wenger@protonmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{ace-wenger}
\linkedin{Aaron Wenger}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
   {Recruitment Team}
   {Michigan Department of Education\\608 W. Allegan\\Lansing MI 48933}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Evaluation and Strategic Research Consultant}
% How the letter is opened
\letteropening{Dear Mr. Judd and Mr. Finkbeiner,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Aaron C. Wenger~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{Why Apply to the MDE?}
I am excited to apply for this research consultant positon and work directly with MDE. My career aspiration is to advance the state of educational measurement and research for the benefit of all students, especially those currently underserved. I believe that this position in the Office of Systems, Evaluation, and Technology serves that end.

In a previous position as a graduate research assistant I collaborated with staff in the MiSTEM Network to evaluate their programs and assess their progress towards yearly goals. I am passionate about the role of measurement and evidence in improving education outcomes for all students.

\lettersection{Why Me?}
In my graduate program, I developed my interest in the role of evidence in educational policy and practice. I learned how to conduct systematic reviews and meta-analyses of published studies to provide the best possible recommendations. I have created research protocols to characterize study designs and evaluate their rigor. To improve the transparency and credibility of my research, I self-taught how to program in R and the basics of data management. 

For me, learning new skills and developing a diverse skill set is an especially enjoyable aspect of research. During my time as a research assistant evaluating educational programs, I engaged in both qualitative (interviews and case studies) and quantitative (descriptive and inferential statistics) methods to draft annual reports of NSF and MDE-funded programs, collaborating with internal and external team members.

\lettersection{What Can I Contribute?}
Aside from my interests, skills, and experience referred to above and in my CV, I bring a developmental and collaborative approach to my work. I have cultivated relationships and collaborations in time as a graduate student, even organizing a new research group for fellow students. I believe that good work is transparent, accessible, and therefore inclusive of current and future colleagues.

I believe that my focus on collaboration, extensive research background, and two years of experience in education evaluation would make me a valuable part of the team. I am grateful for the opportunity to apply and be considered for this position.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}